The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications

### 2018-04-27 paper.tex
Minor change.
Synchronized color, added reference to new review

\newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
\newcommand{\peter}[1]{{\color{blue}{#1}}}
\newcommand{\comment}[1]{{\color{YellowGreen}{#1}}}
\newcommand{\ah}{\hat{a}}
\newcommand{\adagh}{\hat{a}^\dag}

@@

\title{The resurgence of the linear optics quantum interferometer --- recent advances \& applications}

@@

The promises offered by linear optics have spearheaded many \sihui{scientific and} technical advancements. One of the major successes for linear optics is \sihui{the detection of gravitational waves by the LIGO experiments based on the Michelson interferometer \cite{bib:LIGO2015}. The further application of squeezed light to the detectors promises to reduce quantum noise, which currently limits their performance \cite{bib:Barsotti18}. Another advancement is} the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This has increased the scalability of optical implementations of quantum information protocols. Furthermore, it is now possible to have single-photon sources and detectors together with linear-optical networks on a silica chip \cite{bib:Sprengers11, bib:Silverstone14}. Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}.

@@

\peter{
In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built. However, owing to manufacturing imperfections, a precise characterization of these devices may still be needed post-production. One approach for achieving this is via quantum process tomography, discussed in the next section.

@@

While the input-to-output amplitudes of a linear optics network may be efficiently determined (in terms of number of measurements), it does not characterise the full quantum process it implements, which may contain errors in other degrees of freedom.
}

@@

\end{document}

>>>>

\newcommand{\sihui}[1]{{\color{red}{#1}}}
\newcommand{\peter}[1]{{\color{red}{#1}}}
\newcommand{\comment}[1]{{\color{YellowGreen}{#1}}}
\newcommand{\ah}{\hat{a}}
\newcommand{\adagh}{\hat{a}^\dag}

@@

\title{The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications}

@@

The promises offered by linear optics have spearheaded many \sihui{scientific and} technical advancements. One of the major successes for linear optics is \sihui{the detection of gravitational waves by the LIGO experiments based on the Michelson interferometer \cite{bib:LIGO2015}. The further application of squeezed light to the detectors promises to reduce quantum noise, which currently limits their performance \cite{bib:Barsotti18}. Another advancement is} the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This has increased the scalability of optical implementations of quantum information protocols. Furthermore, it is now possible to have single-photon sources and detectors together with linear-optical networks on a silica chip \cite{bib:Sprengers11, bib:Silverstone14}. Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}. \sihui{Experimental advancements and limitations of photonic implementations of quantum information processing are discussed at length in another review \cite{bib:Flamini2018}.}

@@

In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built. However, owing to manufacturing imperfections, a precise characterization of these devices may still be needed post-production. One approach for achieving this is via quantum process tomography, discussed in the next section.

@@

While the input-to-output amplitudes of a linear optics network may be efficiently determined (in terms of number of measurements), it does not characterise the full quantum process it implements, which may contain errors in other degrees of freedom.

@@

\end{document}
i
